Second-Generation Web Interface to Correcting ASR output

### 2018-03-31 2018-ftc-vancouver/webapp.tex
tidy the tabularx source code

\noindent
\begin{tabularx}{\textwidth}{
    @{\hspace{1.5em}}% Space for left bullet
    >{\leavevmode\llap{\textbullet~}\raggedright}% Left bullet + formatting of column
    X% Left column specification
    @{\quad\hspace{1.5em}}% Space between columns + right bullet space
    >{\leavevmode\llap{\textbullet~}\raggedright\arraybackslash}% Right bullet + formatting of column
    X% Right column specification
    @{}% No column space on right
  }
  \em{transcription applications}: & \em{our application}: \\
  (1,2,3) are optimized for the case where there is no transcription available and it
  must be acquired from scratch; &
    always assumes a prior transcription is available; \\
  (1) allow annotation of speakers; &
    assumes all utterances come from the same speaker; \\
  (1,2,3) need no quality control: the user is free to enter whatever
  transcription she pleases and the ultimate measure is her satisfaction; &
    needs the transcription to be accurate because it is used as training data
    for the acoustic model; \\
  (1)\footnote{Transcriber explicitly aligns the text with speech, while the
  other two merely automate addition of timestamps into the transcription.} use
  alignment on the level of phrases, if any; &
    uses alignment on the level of words; \\
  (1,2,3) are user-centric: the user transcribes whatever acoustic data they
  choose; &
    is data-centric: the whole application with all its tools and persons
    revolves around the data set; \\
  (1,2,3) assumes the user wants to transcribe; &
    assume the user wants to listen and possibly read along and we want to
    animate her to submit transcriptions; \\
  (1,2)\footnote{Transcribe supports team co-operation.} has no shared data
  between users; &
    must count with collisions. \\
\end{tabularx}

>>>>

\noindent
\begin{tabularx}{\textwidth}{
    @{\hspace{1.5em}}% Space for left bullet
    >{{\hsize=0.9\hsize}\leavevmode\llap{\textbullet~}\raggedright}% Left bullet + formatting of column
    X% Left column specification
    @{\hspace{0.2em}}
    >{\hsize=0.2\hsize}
    X
    @{\quad\hspace{1.5em}}% Space between columns + right bullet space
    >{\leavevmode\llap{\textbullet~}\raggedright\arraybackslash}% Right bullet + formatting of column
    X% Right column specification
    @{}% No column space on right
  }
  \em{transcription applications}: & & \em{our application}: \\
  are optimized for the case where there is no transcription available and it
  must be acquired from scratch; &
    (1,2,3) &
      always assumes a prior transcription is available; \\

  allow annotation of speakers; &
    (1) &
      assumes all utterances come from the same speaker; \\

  need no quality control: the user is free to enter whatever transcription she
  pleases and the ultimate measure is her satisfaction; &
    (1,2,3) &
      needs the transcription to be accurate because it is used as training data
      for the acoustic model; \\

  use alignment on the level of phrases, if any; &
    (1)\footnote{
        Transcriber explicitly aligns the text with speech, while the
        other two merely automate addition of timestamps into the transcription.
    } &
      uses alignment on the level of words; \\

  are user-centric: the user transcribes whatever acoustic data they choose; &
    (1,2,3) &
      is data-centric: the whole application with all its tools and persons
      revolves around the data set; \\

  assumes the user wants to transcribe; &
    (1,2,3) &
      assume the user wants to listen and possibly read along and we want to
      animate her to submit transcriptions; \\

  has no shared data between users; &
    (1,2)\footnote{Transcribe supports team co-operation.} &
      must count with collisions. \\
\end{tabularx}
